Missing years 2019 and 2020^[Code and data are available at: https://github.com/SANGWOONG-LEE/2016electionanalysis]

### 2022-04-22 outputs/paper/paper.Rmd
Data session writing (1)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
library(tidyverse)
library(dplyr)
library(knitr)
library(scales)
```

# Introduction
First paragraph

Second paragraph

Third paragraph

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
library(tidyverse)
library(dplyr)
library(knitr)
library(scales)
library(modelsummary)
```

# Introduction
First paragraph : broader context for motivation

Second paragraph : some detail about what the paper is about

Third paragraph: a clear gap that needs to be filled

Fourth: what was done, what was found

5: why it is important

@@

For this paper, my aim is to find out changes in U.S citizens' minds regarding government before and after COVID-19 outbreak. Following that, I obtained datasets from U.S GSS 2018 and 2021 since COVID-19 was first reported on 2019. There are numerous surveys about COVID-19, however in order to analyze changes in general thoughts, they are not as appropriate as U.S GSS. Most COVID-19 surveys were specifically aimed for health care fields. For instance, whether healthcare system was enough to cover all patients or not was a major point for most COVID-19 surveys. On the other hand, U.S GSS datasets included more various fields such as national spending on drug, crime and etc, thus it can rather represent more general changes.
Among countless variables existing in U.S GSS, I chose opinions on national spending and government actions. Since I used two different years for comparison, I had to find out which variables were in common, then combined them.

The variables I collected were as followed:
1) National spending on various fields (foreign aids, arms, children, big cities, crime, drug,
education, new energy, environment, fare, healthcare, mass transportation, parks, race, roads, science and social security )

2) Government's actions (income equality, the sick, the poor)

3) Respondents' health

There exists 17 variables in national spending and 3 variables regarding government actions. Since, dealing with all variables in this session would take much spaces, for those that did not change much between 2018 and 2022, I am going to deal with in Appendix.
